Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

% 2. hypothesis

@@

>>>>

% 2. table: left and right

@@

% 3. table: upper and lower

For cases in the upper triangular of \cref{tab:desth}, $E[H_S] < E[H_D]$,
which means most triplets will be turned into adversarial example by HM
to increase the hardness.
%
Although most of such cases end up with model collapse, the preliminary 
result suggests that HM from random to semihard is effective in significantly
improve the robustness without model collapse, at an expected cost on the R@1
performance on benign examples.
